\LARGE \bf ``Those who can't do teach'': Learning Handwriting by Teaching a Robot

### 2014-08-22 main.tex
Rewritten conclusion

>>>>

\subsection{Impact and Conclusion}

We believe this article introduces three noteworthy contributions: an innovative
application of data processing and artificial intelligence for the generation and
learning of hand-written letters suitable for educative purposes; a robotic
system that has been experimentally proven to provide convincing scaffolding for
complex human-robot interactions (teacher-learner social interactions, learning by
demonstration); an initial experimental investigation of what appears to be a
new role for robots in education.

Because it has the strongest impact for the human-robot interaction community,
we would like to develop this last point in particular. The work presented here
investigates a particular role for a robot in the education of handwriting: not
only the robot is actively performing the activity (it draws letters), but it
does so in a way that engages the child in a very specific social role. The child
is the teacher, the robot is the learner: the child must engage in a
(meta-)cognitive relation with the robot to try to understand why the
robot fails and how to help it best.  Here, the robot is not only an activity
facilitator or orchestrator: its physical presence and embodiment induce agency
and anthropomorphizing, and cognitively engage the child into the learning
activity, which we predict to lead to higher learning efficacy.

Also notable, the robot is not used in the usual context of robotics or computer
education, but instead in an activity -- handwriting -- that requires fine
physical skills. In such activities, the embodied nature of the robot makes a
lot of sense (due to motor mimicry, the arm motion for instance is, \emph{by
itself}, part of the teaching). Along those lines, we hope to see more research
on non-STEM educational applications of robotics.

Beyond handwriting, we believe that this work provides a novel perspective on
the role for robots in the education landscape. \emph{Learning by teaching} is a
powerful paradigm because not only its pedagogical efficacy is proven, but it
also positively impacts the child's motivation and self-esteem. We have
discovered that it is also a very relevant context of use for robots. Indeed,
when facing a child with school difficulties, robots can play a role (being the
``even more ignorant student'') that neither the adults nor the peers (because
of the social effects it would induce) can convincingly play.

The strong social impact of early school problems makes research in this field
a certainly useful challenge for HRI.
